\documentclass[letterpaper]{deedy-resume}

\begin{document}

\lastupdated

\namesection{Jamie}{Klassen}{
\urlstyle{same}\url{http://jamieklassen.com} \\ 
\href{mailto:michigan.j.frog@gmail.com}{michigan.j.frog@gmail.com} | 647.206.4576}

\begin{minipage}[t]{0.33\textwidth}

\section{Education} 
\subsection{University of Waterloo}

\descript{BMath in Pure Mathematics}
\location{May 2014 - Aug 2015 | Waterloo, ON}

\sectionspace

\subsection{McGill University}

\descript{BA, Joint Honours Math and Computer Science (partial)}
\location{Sept 2010 - Oct 2013 | Montreal, QC \\ Cum. GPA: 3.96}

\sectionspace

\section{Links} 

Github:// \href{https://github.com/jamieklassen}{\bf jamieklassen} \\
LinkedIn:// \href{https://ca.linkedin.com/in/jamie-klassen-461711b0}
{\bf jamie-klassen-461711b0} \\

\sectionspace

\section{Skills}

\subsection{Programming}

\location{Over 5000 lines:}
Java/Spring/Android \textbullet{}
Python/Django \textbullet{} \LaTeX \textbullet{}
Javascript/Angular \textbullet{} Ruby/Rails \textbullet{} Unix Shell \\
\location{Over 1000 lines:}
C++ \textbullet{} CSS \\
\location{Familiar:}
C \textbullet{} OCaml \textbullet{} Haskell \textbullet{} Perl \textbullet{} R
\textbullet{} Lisp

\sectionspace

\subsection{DevOps}

Concourse \textbullet{} Cloud Foundry \textbullet{} BOSH \textbullet{}
AWS \textbullet{} GCP \textbullet{} Linux (Debian, Ubuntu, Alpine) \& BSD
\textbullet{} Docker \textbullet{} PostgreSQL \textbullet{} MongoDB


\sectionspace

\end{minipage}
\hfill
\begin{minipage}[t]{0.66\textwidth}

\section{Experience}

\runsubsection{Pivotal Software - Cloud Foundry}
\descript{| Software Engineer}

\location{May 2017 – present | Toronto, ON}
Worked in a super awesome product company
\vspace{\topsep}
\begin{tightitemize}
\item Open Source Licensing Tooling - You can see my commits on LicenseFinder!
But also I worked on a Rails app and had to manage a very large amount of data and
building a service that didn't perfectly fit the SaaS paradigm.
\item PFS - Building an open source FaaS built on top of Kubernetes. Really cool!
\end{tightitemize}

\sectionspace

\runsubsection{Pivotal Software - Pivotal Labs}
\descript{| Agile Software Engineer}

\location{Sept 2016 – May 2017 | Toronto, ON}
Worked in a super awesome consulting company
\vspace{\topsep}
\begin{tightitemize}
\item Ford Turbo - Spring microservices, learned Java 8 and used CI/CD and Agile
\item FordPass Android CN and CV - Android, instrumentation tests, figured out
an awesome way to mock time in tests, very large project, refactorings
\item Recon - Internal project, used a lot of awesome Concourse skills in a way
I've never seen anybody else do
\item Audatex Novo Compliance - longer term, worked with client devs, polyglot
C\#/.NET Core Java/Spring and JS/Angular 4 full-stack project integrating with
other teams. Played a major role in defining project requirements, blackbox
definition of predictive models
\end{tightitemize}

\sectionspace

\runsubsection{McGill University - ELVIS Project}
\descript{| Software Developer}

\location{July 2012 – Sept 2013 | Montreal, QC}
The clients (music theory professors) had unclear requirements: use a Python music notation
library to do computer queries on large datasets of sheet music. Myself and one other coder:
\vspace{\topsep}
\begin{tightitemize}
\item Determined general parameters of the client's requirements and refined a collection of
isolated query scripts into a mature, abstract software development framework.
\item Built, deployed and debugged a Django/Javascript (Knockout.js) web app frontend to leverage the
framework, in time for the clients to demonstrate its use at academic conferences.
\end{tightitemize}

\sectionspace

\runsubsection{McGill University - ISMI}
\descript{| Technical Consultant}

\location{July 2012 – Sept 2013 | Montreal, QC}
Faced with a home-rolled semantic database engine with an undocumented web API built by a team
in Germany, I was instructed to build Java servlet which would perform simple XSL transformations.
I:
\begin{tightitemize}
\item Conferred with the client and determined they had far more general needs; they
wanted to make arbitrary queries of this database.
\item In conference with the team from Germany, determined that the most effective
way to meet their needs was a kind of modified ``faceted search”
\item Collaborated with the database engine developer on custom API calls to enable
the new technology
\item Instead of the initial servlet requirement, rapidly prototyped a basic engine in
Python and Tornado
\item Built an image and metadata viewer in Django and Javascript for documents in the database
\end{tightitemize}

\sectionspace

\runsubsection{McGill University - DDMAL}
\descript{| Software Developer}

\location{May - Aug 2011 | Montreal, QC}
Worked on a team of six to create a “Google Books for music” web app. My role was in
creating a user interface to clean up computer-recognized sheet music. I:
\begin{tightitemize}
\item Dove headfirst into an undocumented half-English, half-French codebase of legacy
C++/wxWidgets and figured out how to make a new feature with the existing tools
\item Tested, debugged and worked with firsthand user feedback to clean over 2000
pages worth of music data in a matter of weeks.
\item Wrote a Python script to parse a RelaxNG schema into a basic library for a music-
specialized XML format
\end{tightitemize}

\sectionspace

\end{minipage}

\end{document}
